Diagnosising the sensitivity of grounding line flux to changes in sub-ice shelf melting

### 2019-04-22 draft_v1.tex
new metric paragraph

>>>>

\subsection{A possible metric connecting perturbation and GLF}

The propagation of perturbation is likely determined by the flow regime on the ice shelf, i.e., the change of GLF is controlled by both the perturbation (geometry, stress field) and its surrounding ice dynamic features. To verify this we make the following metric:

\begin{equation}
    \Lambda = \sum_i^I \frac{1}{d_i}\mid cos\theta_i \mid,
    \ref{Lambda}
\end{equation}
where $I$ is the total cell number on GL, $d_i$ is the distance between the perturbation spot and the $i$-th cell on GL, $theta_i$ is the angle difference between the direction of the specified normal stress at the perturbation spot and the flow direction for the $i$-th cell on GL. This metric gives us two possible important factors that impact GLF: 1) the geometric location of perturbation spot(the closer perturbation spots to GL, the larger impact of perturbation on GLF; see the discussion in the following section ``Impacts of near-GL perturbations''), 2) the relationship between ice flow along GL and the buttressing direction we choose at the perturbation spot (the perturbation has more impacts on GLF if the buttressing direction aligned more closely with the ice flow directions on GL).  
Similar to above, we rotate the buttressing direction by 1--180$^\circ$ on top of the $\sigma_{p1}$ direction, and calculate $\Lambda$ for each perturbation spot. From Figure \ref{new_metric_new} we can see that $\Lambda$ has large values when the buttressing directions are close to the $\sigma_{p1}$ direction ($\Delta\phi=0^\circ$ or $\Delta\phi=180^\circ$). This is because, for MISMIP+, the $\sigma+{p1}$ on GL largely controls the GLF (see the quiver plots of principle stresses in the Appendix). For real ice shelves, the pattern of ice flow along GL might be much more complex then of MISMIP+m, resulting in difficulty of predicting GLF using single direction buttressing number.

\begin{figure}
	\centering
    \includegraphics[width=1\linewidth]{figs/new_metric_new.pdf}
    \caption{The standard deviations of $\Psi$ -- a metric for how closely a change in normal stress corresponds with a change in velocity -- at each perturbation point of the MISMIP+ domain, for the case of $\sigma_{nn}=\sigma_{p1}$ (a) and $\sigma_{nn}=\sigma_{p2}$ (b).}
	\label{new_metric_new}
\end{figure}
